---
title: "lab06"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab06}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab06)
library(parallel)
###Raw Data

RNGversion(min(as.character(getRversion()),"3.5.3"))
##old sampler used for backward compatibility
## suppressWarnings() can be used so that the above warning is not displayed
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )

```

# Brute force search
```{r}
#`brute_force_knapsack()`solve the knapsack problem by brute force
#Question How much time does it takes to run the algorithm for n = 16 objects?

#cost of time
timestart<-Sys.time()

#solve the knapsack problem
brute_force_knapsack(x = knapsack_objects[1:16,], W = 10000)

#running time
timeend<-Sys.time()
runningtime<-timeend-timestart
print(runningtime)

```

Question What performance gain could you get by parallelizing brute force search?
when n = 22,Brute force search spend 12 sec,and if we use parallel computing,it will spend only around half of it.

# Dynamic programming
```{r}
#`knapsack_dynamic()`solve the knapsack problem by dynamic programming
#Question How much time does it takes to run the algorithm for n = 500 objects?

#cost of time
timestart<-Sys.time()

#solve the knapsack problem
knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500)

#running time
timeend<-Sys.time()
runningtime<-timeend-timestart
print(runningtime)

```


# Greedy heuristic
```{r}
#`greedy_knapsack()`solve the knapsack problem by greedy heuristic
#Question How much time does it takes to run the algorithm for n = 1000000 objects?

n <- 1000000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )

#cost of time
timestart<-Sys.time()

#solve the knapsack problem
knapsack_dynamic(x = knapsack_objects, W = 10)

#running time
timeend<-Sys.time()
runningtime<-timeend-timestart
print(runningtime)

```

Question What performance gain could you get by trying to improving your code?

This time I added "na.rm = TRUE" into "the_weight=sum(binary_num*x$w)",so it eventually became "the_weight=sum(binary_num*x$w,na.rm = TRUE)". This way, the function would do less work, since I gave more information about the problem. On the condition that the input was "x = knapsack_objects[1:23,]", the running time reduced from 5550ms to 5200ms compared to before.

Improve the time complexity (Brute force search is O(2^n),Dynamic programming is O(n*m) and Greedy heuristic is O(nlogn))


